Towards Enriching Robot's Actions with Affective Movements

### 2017-01-08 HRI-LBR/HRI-LBR2017.tex
Update HRI-LBR2017.tex

The system has been implemented in C++ and interfaced with ROS %TODO Cite, I would like to add them but the space is tight Andy- OK it is not needed
. To fulfill all the requirements, the system was implemented in two different ROS nodes %TODO Here teh term node might be misleading. Maybe ROS node would be better
: one containing the enrichment system, and the second an interface to connect the system with diverse platforms. The system has been tested in two physical platforms, with different degrees of freedom: Triskarino~\cite{angel2013}
 and Keepon\footnote{ The code is available in the repository \url{https://github.com/julianangel/EmotionBot/tree/master/ROS/theatrebot_action_modulation}}.

@@

An Emotional Enrichment System has been designed and implemented to enrich robots' movements with emotions. %To achieve this, it was used an Emotional Execution Tree created from three different types of nodes: simple actions, parallel, and sequential. Andy-This can be left away since it has been already described
This has been tested in two different platforms, with different degrees of freedom, in which emotional actions were conveyed using the same enrichment system but different drivers.

>>>>

The system has been implemented in C++ and interfaced with ROS. To fulfill all the requirements, the system was implemented in two different ROS nodes: one containing the enrichment system, and the second an interface to connect the system with diverse platforms. The system has been tested in two physical platforms, with different degrees of freedom: Triskarino~\cite{angel2013} and Keepon\footnote{The code is available in the repository \url{https://github.com/julianangel/EmotionBot/tree/master/ROS/theatrebot_action_modulation}}.

@@

An Emotional Enrichment System has been designed and implemented to enrich robots' movements with emotions. 
This has been tested in two different platforms, with different degrees of freedom, in which emotional actions were conveyed using the same enrichment system but different drivers.
